\documentclass{article}
\usepackage[utf8]{inputenc}

\title{srs}
\author{mehakp380 }
\date{September 2017}

\begin{document}

\begin{center}
    \large\textbf{{Use Cases:}}
\end{center}
\textbf{Buyer:}
\vspace{0.5cm}
\\Use case:   Registration/Log-in\\
Actor(s):     User              \\                                  
Type:           Primary      \\                                                                                                                       
  Description: In order to surf through the products, users have to register/sign up using registration page. If they are already registered, then they use their username and password to log in into the store. Log-in page checks for their validity, if the entered username and password are already registered in the database then user can proceed to the store.
\vspace{0.5cm}
\\Use case:    Dashboard\\
Actor(s):      User     \\                                               
Type:            Primary       \\                                      
  Description: Users can manage his/her account through dashboard. This will include all the personal details of user like contact details, delivery address and they can also manage their products from dashboard.
\vspace{0.5cm}
\\Use case:    Upload prescription  \\                          
Actor(s):      User   \\                                          
Type:            Primary\\	                                            
Description: Users have two choices, they can either upload their prescription or they can order their goods directly. This case enables the user to upload the prescription for their goods.					
\vspace{0.5cm}
\\Use case:    Place order\\
Actor(s):      User        \\                                          
 Type:            Primary  \\                                          
 Description: Users are also allowed to place an order directly without any prescription. This platform allows them to do so. Users can order all those OTC products which are available in store without a prescription, they can even but these offline.
\vspace{0.5cm}
\\Use case:    Share your experience!\\
Actor(s):      User                \\                           
Type:            Primary     \\                                     
 Description: Users are also provided a choice to share their experience via social media. Our website is integrated with some social media platforms which enables users to share their experience.   
\vspace{0.5cm}
\\Use case:    Review\\
Actor(s):       User     \\                                       
Type:             Primary  \\                                     
 Description:  Users can also give their review of the product they purchased in this section. Suggestions are always welcome. If users find a scope for improvement in the website, they can add their suggestions in this section.
\vspace{0.5cm}
\\Use case:    Cart	\\			                                 
Actor(s):      User   \\                                            
Type:            Primary \\                                           
  Description:  User can alter their orders, they can add or remove the products in the cart. Users can add their OTC products directly to the cart. Once the prescription is analysed and users are given an option to add the products to the cart. Cart is a platform where we can see all our placed orders.\\
\vspace{1.0cm}
\\\textbf{Pharmacist:}
\vspace{0.5cm}
\\Use case:   Registration\\
Actor(s):     Pharmacy/Seller\\                                        
  Type:           Primary        \\                                      
Description:  Any pharmacy who wants to sell their products through our website, they need to submit their license along with details like name of the pharmacy, owner name, etc.. they can use this section to submit license and register their pharmacy store on our website.
\vspace{0.5cm}
\\Use case:    Product inventory\\
Actor(s):    Pharmacy/Seller     \\                                    
 Type:          Primary  \\
Description:  Pharmacy/Seller will be able to list all the products available with them. This inventory will contain Product name, Picture, Details, Expiry, Quantity, etc..
\vspace{0.5cm}
\\Use case:    Seller dashboard\\
Actor(s):    Pharmacy/Seller\\
Type:          Primary\\
Description:  Sellers/Pharmacy can manage their accounts through dashboard. This will also include dealing with orders, prescriptions and admin messages. They can even edit their profiles and save changes through this section.
\vspace{0.5cm}
\\Use case:    Delivery Status\\
Actor(s):      Pharmacy/Sellers  \\                                   
  Type:            Primary         \\                            
 Description:  Pharmacy management/Sellers will be able to see all the products dispatched from the store and their delivery status. Once the product is delivered, a confirmation message is given both to pharmacy and user.
\vspace{0.5cm}
\\Use case:    Contact user\\
Actor(s):      Pharmacy/Seller  \\                                
   Type:            Primary  \\                               
Description:  Once the prescription has been accepted by the pharmacy/seller, the management will be able to see the contact details of the consumer and then if it is necessary, contact the user. The contact details would be taken from the user’s profile.\\
\vspace{1.0cm}
\\\textbf{Admin:}
\vspace{0.5cm}
\\Use case:    Admin dashboard\\
Actor(s):     Administrator   \\                                         
Type:           Primary \\                                            
 Description:  Admin  can manage their accounts through this platform. This page includes tasks like authenticating and verifying the license of the pharmacy. 
\vspace{0.5cm}
\\Use case:    Track review \\
Actor(s):      Administrator  \\                                         
Type:            Primary      \\                           
Description:  Admin can view all those reviews given by the customers to different pharmacies/sellers. According to these reviews admin will act. If the reviews are quite negative admin may take action against pharmacies/sellers.                                                                                                        


\end{document}
